Verifying Concurrent Search Structure Templates for C Programs using VST

### 2023-04-18 concurrency/CONCUR 2023/paper.tex
fix breakage

\begin{figure}[h]
	\centering
	\begin{mathpar}
		% spec of inRange
		{\color{blue}
			\left\{ 
			\begin{array}{c}
				\texttt{pn}\mapsto\texttt{n} \ast \texttt{n}\mapsto\texttt{t} \ast \texttt{t} \mapsto \texttt{(k', v', l, r)} 
			\end{array}
			\right\}
		}
		\\ 
		\texttt{findNext(pn, k)} 
		\\
		{\color{blue}
			\left\{\exists \  \texttt{res n'.}
			\begin{array}{c}
				\texttt{pn}\mapsto\texttt{n} \ast \texttt{n}\mapsto\texttt{t} \ast \texttt{t} \mapsto \texttt{(k', v', l, r)} \\\  
				\ast \ \texttt{(if res then } \texttt{(l = n'} \land \texttt{k < k')} \lor \texttt{(r = n'} \land \texttt{k > k')} \texttt{ else } \texttt{(n' = n} \land \texttt{k = k'))}
			\end{array}
			\right\}
		}
	\end{mathpar}
	\caption{Specification of \texttt{findNext} for the lock-coupling and give-up templates}
	\label{fig:findNext_lock}
\end{figure}

@@

\begin{figure}
	\centering
\begin{mathpar}
	% spec of inRange
	{\color{blue}
		\left\{ 
		\begin{array}{c}
			\texttt{pn}\mapsto\texttt{n} \ \ast \texttt{n}\mapsto\texttt{t} \ \ast \ \texttt{n}\mapsto\texttt{min} \ \ast \ \texttt{n->max}
		\end{array}
		\right\}
	}
	\\ 
	\texttt{inRange(pn, k)} 
	\\
	{\color{blue}
		\left\{\exists \  \texttt{res.}
		\begin{array}{c}
			 \ \texttt{pn}\mapsto\texttt{n} \ \ast \ \texttt{n}\mapsto\texttt{t} \ \ast \ \texttt{n}\mapsto\texttt{min} \ \ast \ \texttt{n}\mapsto\texttt{max}\  \\ 
			 \ \ast  \ \texttt{(if res then } \texttt{(min < x} \land \texttt{x < max)} \land \texttt{(x} \leq \texttt{min} \lor \texttt{x} \geq \texttt{max))}
		\end{array}
		\right\}
	}
\end{mathpar}
\caption{Specification of \texttt{inRange} for the give-up template}
\label{fig:inRange_giveup}
\end{figure}

\begin{figure}
	\centering
	\begin{mathpar}
	%spec of insertOp
	{\color{blue}
		\left\{ 
		\begin{array}{c}
			\texttt{pn}\mapsto\texttt{n} \ \ast \ \texttt{n}\mapsto\texttt{t} \  \ast \ \texttt{n}\mapsto\texttt{min} \ \ast \ \texttt{n}\mapsto\texttt{max}
		\end{array}
		\right\}
	}
	\\
	\texttt{insertOp(pn, k, v)}
	\\
	{\color{blue}
	\left\{\exists \ \texttt{t' l r lk1 lk2}. 
	\begin{array}{c}
		\ \texttt{pn}\mapsto\texttt{n} \ \ast \ \texttt{n}\mapsto\texttt{t'} \ \ast \ \texttt{t'}\mapsto \texttt{(k, v, l, r)} \\ 
		\ \ast \ \texttt{l} \mapsto \texttt{(NULL, lk1, (min, x))} \ \ast \ \texttt{r} \mapsto \texttt{(NULL, lk2, (x, max))}
	\end{array}
	\right\}
	}
\end{mathpar}
\caption{Specification of \texttt{insertOp} for the give-up template}
\label{fig:insertOp_giveup}
\end{figure}

>>>>

\begin{figure}[h]
	\centering
	\begin{mathpar}
		% spec of inRange
		{\color{blue}
			\left\{ 
			\begin{array}{c}
				\texttt{pn}\mapsto\texttt{n} \ast \texttt{n}\mapsto\texttt{t} \ast \texttt{t} \mapsto \texttt{(k', v', l, r)} 
			\end{array}
			\right\}
		}
		\\ 
		\texttt{findNext(pn, k)} 
		\\
		{\color{blue}
			\left\{\exists \  \texttt{res n'.}
			\begin{array}{c}
				\texttt{pn}\mapsto\texttt{n} \ast \texttt{n}\mapsto\texttt{t} \ast \texttt{t} \mapsto \texttt{(k', v', l, r)} \\\  
				\ast \ \texttt{(if res then } \texttt{(l = n'} \land \texttt{k < k')} \lor \texttt{(r = n'} \land \texttt{k > k')} \texttt{ else } \texttt{(n = n'} \land \texttt{k = k'))}
			\end{array}
			\right\}
		}
	\end{mathpar}
	\caption{Specification of \texttt{findNext} for the lock-coupling and give-up templates}
	\label{fig:findNext_lock}
\end{figure}

@@

\begin{figure}
	\centering
\begin{mathpar}
	% spec of inRange
	{\color{blue}
		\left\{ 
		\begin{array}{c}
			\texttt{pn}\mapsto\texttt{n} \ \ast \texttt{n}\mapsto\texttt{(t, lock, min, max)} 
		\end{array}
		\right\}
	}
	\\ 
	\texttt{inRange(pn, k)} 
	\\
	{\color{blue}
		\left\{\exists \  \texttt{res.}
		\begin{array}{c}
			 \ \texttt{pn}\mapsto\texttt{n} \ \ast \ \texttt{n}\mapsto\texttt{(t, lock, min, max)} \  \\ 
			 \ \ast  \ \texttt{(if res then } \texttt{(min < k} \land \texttt{k < max)} \land \texttt{(k} \leq \texttt{min} \lor \texttt{k} \geq \texttt{max))}
		\end{array}
		\right\}
	}
\end{mathpar}
\caption{Specification of \texttt{inRange} for the give-up template}
\label{fig:inRange_giveup}
\end{figure}

\begin{figure}
	\centering
	\begin{mathpar}
	%spec of insertOp
	{\color{blue}
		\left\{ 
		\begin{array}{c}
			\texttt{pn}\mapsto\texttt{n} \ \ast \ \texttt{n}\mapsto\texttt{t} \  \ast \ \texttt{n}\mapsto\texttt{min} \ \ast \ \texttt{n}\mapsto\texttt{max}
		\end{array}
		\right\}
	}
	\\
	\texttt{insertOp(pn, k, v)}
	\\
	{\color{blue}
	\left\{\exists \ \texttt{t' l r lk1 lk2}. 
	\begin{array}{c}
		\ \texttt{pn}\mapsto\texttt{n} \ \ast \ \texttt{n}\mapsto\texttt{t'} \ \ast \ \texttt{t'}\mapsto \texttt{(k, v, l, r)} \\ 
		\ \ast \ \texttt{l} \mapsto \texttt{(NULL, lk1, (min, k))} \ \ast \ \texttt{r} \mapsto \texttt{(NULL, lk2, (k, max))}
	\end{array}
	\right\}
	}
\end{mathpar}
\caption{Specification of \texttt{insertOp} for the give-up template}
\label{fig:insertOp_giveup}
\end{figure}
